Plots and tables summarizing results of Poisson simulations

### 2018-12-20 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

This is the function used to simulate the "Spikes" data sets:

```{r spikes-function, fig.height=5, fig.width=10}
mu.s <- spike.f(t)
plot(t,mu.s,xlab = "",ylab = "",type = "l",
     main = "Spikes intensity function")
```

@@

```{r spikes-violin-plots, fig.height=5, fig.width=7}
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
					                 mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
n     <- length(mise.ash.s.1)
pdat1 <- data.frame(method = rep(c("SMASH","BMSM","HF"),each = n),
 				    mise   = c(mise.ash.s.1,mise.BMSM.s.1,mise.hf.ti.r.s.1))
p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
      coord_flip()
      labs(x = "",y = "MISE") +
     theme(axis.line = element_blank(),
           axis.ticks.y = element_blank())
```

@@

### Angles data

@@

### Heavisine data

@@

### Bursts data

@@

### Clipped Blocks data

@@

### Bumps data

>>>>

This is the function used to simulate the "Spikes" data sets at
different ranges of intensities:

```{r plot-spikes-function, fig.height=4, fig.width=8}
mu.s <- spike.f(t)
plot(t,mu.s,xlab = "",ylab = "",type = "l",
     main = "Spikes intensity function")
```

@@

```{r spikes-violin-plots, fig.height=5, fig.width=7}
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
					                 mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
m     <- length(mise.ash.s.1)
pdat1 <- data.frame(method = rep(c("SMASH","BMSM","HF"),each = m),
 				    mise   = c(mise.ash.s.1,mise.BMSM.s.1,mise.hf.ti.r.s.1))
p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
      coord_flip()
      labs(x = "",y = "MISE") +
     theme(axis.line = element_blank(),
           axis.ticks.y = element_blank())
```

@@

Angles data
-----------

This is the function used to simulate the "Angles" data sets at
different ranges of intensities:

```{r plot-angles-function, fig.height=4, fig.width=8}
mu.ang <- dop.f(t)
sig <- ((2 * t + 0.5) * (t <= 0.15)) +
  ((-12 * (t - 0.15) + 0.8) * (t > 0.15 & t <= 0.2)) +
  0.2 * (t > 0.2 & t <= 0.5) + 
  ((6 * (t - 0.5) + 0.2) * (t > 0.5 & t <= 0.6)) +
  ((-10 * (t - 0.6) + 0.8) * (t > 0.6 & t <= 0.65)) +
  ((-0.5 * (t - 0.65) + 0.3) * (t > 0.65 & t <= 0.85)) +
  ((2 * (t - 0.85) + 0.2) * (t > 0.85))
mu.ang <- 3/5 * ((5/(max(sig) - min(sig))) * sig - 1.6) - 0.0419569
plot(t,mu.ang,xlab = "",ylab = "",type = "l",
     main = "Angles intensity function")
```

@@

Heavisine data
--------------

This is the function used to simulate the "Heavisine" data sets at
different ranges of intensities:

```{r plot-heavisine-function, fig.height=4, fig.width=8}
heavi <- 4 * sin(4 * pi * t) - sign(t - 0.3) - sign(0.72 - t)
mu.hs <- heavi/sqrt(var(heavi)) * 1 * 2.99/3.366185
mu.hs <- mu.hs - min(mu.hs)
plot(t,mu.hs,xlab = "",ylab = "",type = "l",
     main = "Heavisine intensity function")
```

@@

Bursts data
-----------

This is the function used to simulate the "Bursts" data sets at
different ranges of intensities:

```{r plot-bursts-function, fig.height=4, fig.width=8}
I_1 <- exp(-(abs(t - 0.2)/0.01)^1.2) * (t <= 0.2) +
       exp(-(abs(t - 0.2)/0.03)^1.2) * (t > 0.2)
I_2 <- exp(-(abs(t - 0.3)/0.01)^1.2) * (t <= 0.3) +
       exp(-(abs(t - 0.3)/0.03)^1.2) * (t > 0.3)
I_3 <- exp(-(abs(t - 0.4)/0.01)^1.2) * (t <= 0.4) +
       exp(-(abs(t - 0.4)/0.03)^1.2) * (t > 0.4)
mu.bur <- 2.99/4.51804 * (4 * I_1 + 3 * I_2 + 4.5 * I_3)
plot(t,mu.bur,xlab = "",ylab = "",type = "l",
     main = "Bursts intensity function")
```

@@

Clipped Blocks data
-------------------

This is the function used to simulate the "Clipped Blocks" data sets at
different ranges of intensities:

```{r plot-cb-function, fig.height=4, fig.width=8}
pos   <- c(0.1,0.13,0.15,0.23,0.25,0.4,0.44,0.65,0.76,0.78,0.81)
hgt   <- 2.88/5 * c(4,-5,3,-4,5,-4.2,2.1,4.3,-3.1,2.1,-4.2)
mu.cb <- rep(0,n)
for (j in 1:length(pos))
  mu.cb <- mu.cb + (1 + sign(t - pos[j])) * (hgt[j]/2)
mu.cb[mu.cb < 0] <- 0
plot(t,mu.cb,xlab = "",ylab = "",type = "l",
     main = "Clipped Blocks intensity function")
```

@@

Bumps data
----------

This is the function used to simulate the "Bumps" data sets at
different ranges of intensities:

```{r plot-bumps-function, fig.height=4, fig.width=8}
pos  <- c(0.1,0.13,0.15,0.23,0.25,0.4,0.44,0.65,0.76,0.78,0.81)
hgt  <- 2.97/5 * c(4,5,3,4,5,4.2,2.1,4.3,3.1,5.1,4.2)
wth  <- c(0.005,0.005,0.006,0.01,0.01,0.03,0.01,0.01,0.005,0.008,0.005)
mu.b <- rep(0, n)
for (j in 1:length(pos))
  mu.b <- mu.b + hgt[j]/((1 + (abs(t - pos[j])/wth[j]))^4)
plot(t,mu.b,xlab = "",ylab = "",type = "l",
     main = "Bumps intensity function")
```
